\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change

### 2014-10-24 manuscript/ms_MicroMeso.Rnw
updated table caption

\documentclass[12pt]{article}
\usepackage{graphics}
\usepackage{graphicx, verbatim}
\usepackage{amssymb,amsmath}
% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
\usepackage{authblk}
\textwidth=6.2in
\textheight=8.5in
%\parskip=.3cm
\oddsidemargin=.1in
\evensidemargin=.1in
\headheight=-.3in

@@

\[ 
logit(s) = \beta_{0,t} + \beta_{s,t}x + \beta_{Q} + \beta_{c,1}\theta_{1,t}\\
+ \cdots +  \beta_{c,i}\theta_{i,t} + \varepsilon_{t}
\]

@@

\[ 
x_{t+1} = \beta_{0,t} + \beta_{s,t}x_{t} + \beta_{Q} + \beta_{c,1}\theta_{1,t}\\
+ \cdots +  \beta_{c,i}\theta_{i,t} + \varepsilon_{t}
\]

\noindent where $x$ is genet size and all other paramters are as described for the survival regression. For the quadrat-level approach we modeled growth as a process describing proportional cover within a quadrat at time $t+1$ as a function of proportional cover at time $t$ and climate covariates. Thus, instead of a gaussian process, with a normal likelihood, we modeled growth at the quadrat level as above but with a beta likelihood.

@@

>>>>

\documentclass[12pt]{article}
\usepackage{graphics}
\usepackage{graphicx, verbatim}
\usepackage{amssymb,amsmath}
\usepackage{tabularx}
% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
\usepackage{authblk}
\textwidth=6.2in
\textheight=8.5in
%\parskip=.3cm
\oddsidemargin=.1in
\evensidemargin=.1in
\headheight=-.3in

@@

\begin{equation}
logit(s) = \beta_{0,t} + \beta_{s,t}x + \beta_{Q} + \beta_{c,1}\theta_{1,t}\\
+ \cdots +  \beta_{c,i}\theta_{i,t} + \varepsilon_{t}
\end{equation}

@@

\begin{equation}
x_{t+1} = \beta_{0,t} + \beta_{s,t}x_{t} + \beta_{Q} + \beta_{c,1}\theta_{1,t}\\
+ \cdots +  \beta_{c,i}\theta_{i,t} + \varepsilon_{t}
\end{equation}

\noindent where $x$ is genet size and all other paramters are as described for the survival regression. For the quadrat-level approach we modeled growth as a process describing proportional cover within a quadrat at time $t+1$ as a function of proportional cover at time $t$ and climate covariates. Thus, instead of a gaussian process, with a normal likelihood, we modeled growth at the quadrat level as above but with a beta likelihood and a logit link to the linear predictors.

@@

\section{Results}
We assessed the statistical importance of the climate covariates included the final vital rate regressions by comparing the residual deviance of models with climate covariates and temporal random effects, climate covariates only, and temporal random effects only. When a model includes climate covariates, this comparison shows the relative contribution of the climate covariates in explaining the total interannual variability (Adler et al. 2012).

<<echo=FALSE,results=tex>>=
library(xtable)
growthSSRTable <- read.csv("../montana/quadBM/vitalRateRegressions/finalModels/growthClimateContributionTable.csv")
survivalSSRTable <- read.csv("../montana/quadBM/vitalRateRegressions/finalModels/survivalClimateContributionTable.csv")
colonizationSSRTable <- read.csv("../montana/quadBM/vitalRateRegressions/finalModels/colonizationClimateContributionTable.csv")

growthSSRTable[,3:6] <- apply(X = growthSSRTable[,3:6], MARGIN = 2, FUN = function(x){round(x, digits = 2)})
survivalSSRTable[,3:6] <- apply(X = survivalSSRTable[,3:6], MARGIN = 2, FUN = function(x){round(x, digits = 2)})
colonizationSSRTable[,3:6] <- apply(X = colonizationSSRTable[,3:6], MARGIN = 2, FUN = function(x){round(x, digits = 2)})

growthSSRTable$Species <- as.character(growthSSRTable$Species)
survivalSSRTable$Species <- as.character(survivalSSRTable$Species)
colonizationSSRTable$Species <- as.character(colonizationSSRTable$Species)

allTableQBM <- rbind(c("Growth", rep("", times=5)), growthSSRTable, 
                     c("Survival", rep("", times=5)), survivalSSRTable, 
                     c("Colonization", rep("", times=5)), colonizationSSRTable) 
colnames(allTableQBM) <- c("", "N", "Constant model", "Climate model", "Full model", "Contribution of climate covariates")

print(xtable(allTableQBM, align=c("l", "l", "l", "l", "l", "l", "X"), 
             caption="The proportion of interannual variability in  vital rates explained by the climate covariates. The contribution is defined as: (Climate model - Constant Model)/(Full model - Constant model). Note that in some cases this will be slightly negative where DIC selected a model with climate covariates but a model without climate covariates had a very similar DIC value."), 
      tabular.environment="tabularx", caption.placement="top",
      width="\\textwidth", include.rownames=FALSE)
@

### 2014-10-24 manuscript/ms_MicroMeso.tex
updated table caption

% latex table generated in R 3.1.0 by xtable 1.7-3 package
% Fri Oct 24 17:26:36 2014
\begin{table}[ht]
\centering
\caption{The proportion of interannual variability in  vital rates explained by the climate covariates.} 
\begin{tabularx}{\textwidth}{lllllX}
  \hline
 & N & Constant model & Climate model & Full model & Contribution of climate covariates \\ 
  \hline
Growth &  &  &  &  &  \\ 
  BOGR & 213 & -881.25 & -881.25 & -938.35 & 0 \\ 
  HECO & 171 & -1365.35 & -1372.06 & -1381.61 & 0.41 \\ 
  PASM & 217 & -2107.02 & -2116.98 & -2164.8 & 0.17 \\ 
  POSE & 197 & -1503.69 & -1502.32 & -1551.44 & -0.03 \\ 
  Survival &  &  &  &  &  \\ 
  BOGR & 218 & 44.62 & 44.62 & 44.53 & 0 \\ 
  HECO & 179 & 51.21 & 51.21 & 51.01 & 0 \\ 
  PASM & 221 & 40.14 & 40.14 & 40.51 & 0 \\ 
  POSE & 204 & 46.41 & 46.41 & 46.25 & 0 \\ 
  Colonization &  &  &  &  &  \\ 
  BOGR & 29 & 38.32 & 39.24 & 44.53 & 0.15 \\ 
  HECO & 68 & 75.78 & 75.78 & 51.01 & 0 \\ 
  PASM & 26 & 32.35 & 32.35 & 40.51 & 0 \\ 
  POSE & 43 & 54.05 & 54.05 & 46.25 & 0 \\ 
   \hline
\end{tabularx}
\end{table}

>>>>

% latex table generated in R 3.1.0 by xtable 1.7-3 package
% Fri Oct 24 17:36:45 2014
\begin{table}[ht]
\centering
\caption{The proportion of interannual variability in  vital rates explained by the climate covariates. The contribution is defined as: (Climate model - Constant Model)/(Full model - Constant model). Note that in some cases this will be slightly negative where DIC selected a model with climate covariates but a model without climate covariates had a very similar DIC value.} 
\begin{tabularx}{\textwidth}{lllllX}
  \hline
 & N & Constant model & Climate model & Full model & Contribution of climate covariates \\ 
  \hline
Growth &  &  &  &  &  \\ 
  BOGR & 213 & -881.25 & -881.25 & -938.35 & 0 \\ 
  HECO & 171 & -1365.35 & -1372.06 & -1381.61 & 0.41 \\ 
  PASM & 217 & -2107.02 & -2116.98 & -2164.8 & 0.17 \\ 
  POSE & 197 & -1503.69 & -1502.32 & -1551.44 & -0.03 \\ 
  Survival &  &  &  &  &  \\ 
  BOGR & 218 & 44.62 & 44.62 & 44.53 & 0 \\ 
  HECO & 179 & 51.21 & 51.21 & 51.01 & 0 \\ 
  PASM & 221 & 40.14 & 40.14 & 40.51 & 0 \\ 
  POSE & 204 & 46.41 & 46.41 & 46.25 & 0 \\ 
  Colonization &  &  &  &  &  \\ 
  BOGR & 29 & 38.32 & 39.24 & 44.53 & 0.15 \\ 
  HECO & 68 & 75.78 & 75.78 & 51.01 & 0 \\ 
  PASM & 26 & 32.35 & 32.35 & 40.51 & 0 \\ 
  POSE & 43 & 54.05 & 54.05 & 46.25 & 0 \\ 
   \hline
\end{tabularx}
\end{table}
